---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%",
    eval = FALSE
)
```

# clix

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

A custom CLI implementation that bundles 

- messages (in the broader sense)
- querying for user input
- executing the implications of a given user input

## Installation

You can install the development version of clix from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rappster/clix")
```

## Why?

When developing a new package I often find myself developing the "same little
CLI helpers" (a mix of messages, user input and implications of that input) over
and over again.

So this is primarily just a means of "DRY" for my own work. 

But of course I also hope it's useful for someone else out there.

## How?

The main functions all start with `ask_*()`. 

These bundle

- messages (in the broader sense)
- querying for user input
- executing the implications of a given user input

I felt like even with superb CLI tooling such as
[{cli}](https://cli.r-lib.org/index.html) those out-of-the-box bundles are
typically still missing - or I just didn't find them yet `r emo::ji("wink")`

Currently, there's only on of these implemented yet: `ask_dir_create()`

## Simple example

I often run into situations where I might **expect** a directory to already
exist (because I might have created it while developing something). However, in
"clean start" scenarios (which might be the case when using your package in
production context) this might not be the case.

So here's a CLI-based way to handle such situations.

Let's create a temporary directory first.

```{r, eval = TRUE}
path <- fs::path(tempdir(), "a/b/c")
```

Then we'll load the package

```{r, eval = TRUE}
library(clix)
```

### Directory does not exist yet

```{r exists-no}
path <- ask_dir_create(dir = path)
# ── Directory check ──────────────────────────────────────────
# Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# does not exist yet.
# 
# Do you want to create it?
# 
# Answering Yes implies the following:
# • Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# will be created
# 
# 
# 1: Yes
# 2: No
# 3: Let me start over
# 4: Exit
```

Answer with an input of 1 ("Yes")

```{r exists-no-selection-yes}
# Selection: 1
# ✓ Directory /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c created.

path %>% fs::dir_exists()
```

### Directory already not exist yet

```{r exists-yes}
ask_dir_create(dir = path)
# ── Directory check ──────────────────────────────────────────
# Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# already exists.
# 
# There is nothing to do.
```

### Directory does not exist yet and you want to keep it that way

Let's make sure the temp dir is deleted again before moving on

```{r}
path %>% fs::dir_delete()
```

Answer with "No" (input = 2)

```{r}
ask_dir_create(dir = path)
# ── Directory check ──────────────────────────────────────────
# Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# does not exist yet.
# 
# Do you want to create it?
# 
# Answering Yes implies the following:
# • Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# will be created
# 
# 
# 1: Yes
# 2: No
# 3: Let me start over
# 4: Exit
```

```{r}
# Selection: 2
# ! Directory '/var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c' was not created
# Warning message:
# In throw_warning(., .console = TRUE) :
#   Directory '/var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c' was not created
```

Answer with "Let me start over" (input = 3)

```{r}
ask_dir_create(dir = path)
# ── Directory check ──────────────────────────────────────────
# Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# does not exist yet.
# 
# Do you want to create it?
# 
# Answering Yes implies the following:
# • Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# will be created
# 
# 
# 1: Yes
# 2: No
# 3: Let me start over
# 4: Exit
```

```{r}
# Selection: 3
# Starting over...
#  
# 1: Yes
# 2: No
# 3: Let me start over
# 4: Exit
```

Answer with "Exit" (input = 4)

```{r}
ask_dir_create(dir = path)
# ── Directory check ──────────────────────────────────────────
# Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# does not exist yet.
# 
# Do you want to create it?
# 
# Answering Yes implies the following:
# • Directory
# /var/folders/r1/_3hsv89s6rq2vl9nm31jjk700000gn/T/Rtmpyl8rUK/a/b/c
# will be created
# 
# 
# 1: Yes
# 2: No
# 3: Let me start over
# 4: Exit
```

```{r}
# Selection: 4
# Exiting
```
